Timely Object Recognition

### 2012-06-01 writeups/nips12/technical.tex

We evaluate two ways of updating probabilities: \emph{direct} and \emph{MRF}.
In the \emph{direct} way, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
This means that an observation of class $i$ does not influence the estimated probability of any class but $C_i$.
$score(C_i)$ for $a_{{det}_i}$ is obtained by training a probabilistic classifier on the detections output.
$score(C_i)$ for $a_{gist}$ is obtained by training probabilistic classifiers on the GIST feature, for all classes.

In the \emph{MRF} way, we employ a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:figure1}, with the observation nodes set to $score(C_i)$ appropriately, or considered unobserved.

>>>>

We evaluate two approaches of updating probabilities: \emph{direct} and \emph{MRF}.
In the \emph{direct} method, $P(C_i|\mathbf{o}) = score(C_i)$ if $\mathbf{o}$ includes the observations for class $C_i$ and $P(C_i|\mathbf{o}) = P(C_i)$ otherwise.
This means that an observation of class $i$ does not influence the estimated probability of any class but $C_i$.
$score(C_i)$ for $a_{{det}_i}$ is obtained by training a probabilistic classifier on the detections output.
$score(C_i)$ for $a_{gist}$ is obtained by training probabilistic classifiers on the GIST feature, for all classes.

The \emph{MRF} approach employs a pairwise fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:figure1}, with the observation nodes set to $score(C_i)$ appropriately, or considered unobserved.
